snpArcher: FASTQ -> VCF workflow for WGS data

### 2023-03-21 DRAFT_DNA_methylation.Rmd
added YV revisions

---
title: 'DNA Methylation Analyses'
subtitle: '*Steven Roberts*, *Sam White*, and ............ '
bibliography: DNA-Methylation.bib
---

@@

```{r meth-bp, echo = FALSE, out.width = "70%", fig.align = "center"}
knitr::include_graphics("images/meth-bp-chart.png")
```

>>>>

---
title: 'DNA Methylation Analyses'
subtitle: '*Steven Roberts*, *Sam White*, and *Yaamini Venkataraman*'
bibliography: DRAFT_DNA_methylation/DNA-Methylation.bib
---

@@

```{r meth-bp, echo = FALSE, out.width = "70%", fig.align = "center"}
knitr::include_graphics("DRAFT_DNA_methylation/meth-bp-chart.png")
```
